%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
    \cventry
    {Software Engineering Intern} % Job title
    {JP Morgan Chase} % Organization
    {Houston, TX\newline Plano, TX} % Location
    {Jun. - Aug. 2022 - 2025} % Date(s)
    {
         \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {\textbf{2025:} Delivered multiple high-impact projects at JP Morgan Chase affecting \textbf{1,000+ engi\-neers} across Chase Digital and \textbf{85M+ con\-sumers}:
          \begin{itemize}
            \item Released scripts to export and normalize 100+ Akamai CDN properties into Terraform modules with dynamic \texttt{.tfvars}, indi\-rectly impacting 85M+ con\-sumers.
            \item Architected an Agentic RAG data-ingestion pipeline for 1,000+ engi\-neers across Chase Digital to search internal docs with multi\-modal embeddings and role-specific prompt engi\-neering.
            \item \textit{Technologies: Python,\allowbreak\ Terraform,\allowbreak\ Akamai APIs,\allowbreak\ LangChain,\allowbreak\ Azure OpenAI,\allowbreak\ PostgresSQL (Backend);\allowbreak\ AWS OpenSearch,\allowbreak\ S3,\allowbreak\ Aurora (Infrastructure);\allowbreak\ Bash (DevOps)}
          \end{itemize}
          }
          \item { \textbf{2024:} Built tooling and models to accelerate backend operations, \textbf{halving time taken} for production bug fixes:
          \begin{itemize}
            \item Designed full-stack web tools automating parameterized batch jobs, halving time taken of SQL data migration and production bug fixes.
            \item Developed time-series forecasting model with \textbf{5.38\% SMAPE} incorporating macro\-economic data.
            \item \textit{Technologies: Java,\allowbreak\ Spring Boot,\allowbreak\ Python,\allowbreak\ Pandas,\allowbreak\ Facebook Prophet,\allowbreak\ OracleSQL (Backend);\allowbreak\ React (Frontend)}
          \end{itemize}
            }
            \item { \textbf{2023:} Delivered a full-stack analytics dashboard for the Fundamental Review of the Trading Book \textbf{(FRTB)} team, enabling comparison of trader behavior and performance against Market Risk benchmarks.
            \begin{itemize}
            \item Implemented dynamic filtering and historical drill-down capabilities to support detailed analytics.
            \item Enhanced test team’s ability to identify trading patterns and risk deviations in real time, improving decision-making for market risk assessment and compliance.
            \item \textit{Technologies: Python,\allowbreak\ Pandas,\allowbreak\ Tornado (Backend);\allowbreak\ React,\allowbreak\ JavaScript (Frontend);\allowbreak\ JPMC Private Cloud (Infrastructure)} 
            \end{itemize}
            }
            \item{ \textbf{2022:} Deployed an interactive ML monitoring interface for JPMC Quants to track model training jobs and deployment status, serving as an internal alternative to Comet.com.
            \begin{itemize}
            \item \textit{Technologies: Jupyter Notebooks,\allowbreak\ Amazon SageMaker \& CloudWatch (Backend);\allowbreak\ Voila,\allowbreak\ ipywidgets,\allowbreak\ Perspective.js (Frontend)}
            \end{itemize}
            }
          \end{cvitems}
        }
        \vspace{3mm}
%---------------------------------------------------------
\cventry
  {Intramural Flag Football Referee \& Supervisor} % Job title
  {Texas A\&M University Department of Recreational Sports} % Organization
  {College Station, TX} % Location
  {Jan. 2023 -- Dec. 2024} % Date(s)
  { 
    \begin{cvitems}   
      \item{
      \textbf{Supervisor:} Improved participant experience and operational efficiency to support \textbf{14,000+ students} per semester.
      \begin{itemize}
      \item Continued refereeing duties while additionally managing referee teams, scheduling games, and overseeing tournaments.
      \item Mentored promising referees through targeted training sessions and one-on-one coaching, enabling many to advance to supervisory roles.
      \end{itemize}
      }
      \item{
      \textbf{Referee:} Improved participant experience support \textbf{14,000+ students} per semester.
      \begin{itemize}
      \item Officiated intramural flag football games, ensuring fair play and enforcing rules.
      \item Recognized for superior conflict management skills and rules knowledge; selected for special events and regional tournaments.
      \end{itemize}
      }
    \end{cvitems}
  }
  \vspace{3mm}
%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Lumen Technologies} % Organization
    {Houston, TX} % Location
    {Jun. 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a Python program to generate daily flat files for logging and reporting purposes.
      \begin{itemize}
      \item \textit{Technologies: Python (Backend); Bash, Unix (DevOps)}
      \end{itemize}
      }
      \item{Created shell scripts to reset database values monthly, preventing data over-accumulation and maintaining system performance.
      \begin{itemize}
      \item \textit{Technologies: MySQL (Backend); Bash, Unix (DevOps)}
      \end{itemize}
      }
      \item {Modified SQL scripts to accurately generate billing reports for \textbf{10,000+ customers}.
      \begin{itemize}
      \item \textit{Technologies: MySQL (Backend)}
      \end{itemize}
      }
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}

%---------------------------------------------------------
  % \cventry
  %   {Student Leader - ApplyAI} % Job title
  %   {AI4ALL} % Organization
  %   {College Station, Texas} % Location
  %   {Jan. 2023 - Aug. 2024} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Facilitated Apply AI events including program launch, proposal and final presentations, social events, and workshops.}
  %       \item {Assisted 4 Apply AI student groups, with 4 students per group, by managing their projects and working with their teammates and mentor to provide a deliverable by the end of the program.}
  %       \item {Used Python, Teachable Machines, \& Jupyter Notebooks to help students understand concepts of algorithms and train machine learning models.}
  %     \end{cvitems}
  %   }
    


% %---------------------------------------------------------
 % \cventry
 %   {iOS App Developer} % Job title
 %   {TAMU Computer Science \& Engineering} % Organization
 %   {College Station, Texas} % Location
 %   {Feb. 2021 - Apr. 2021} % Date(s)
 %   {
 %     \begin{cvitems} % Description(s) of tasks/responsibilities
 %       \item {Implemented Kroger REST Product and Location API functionality into a recipe app so a specific location can be selected and requisite products can be put into a cart to purchase for recipe development.}
  %      \item {Enabled 64-bit encryption for interacting with the Kroger Product Search API.} 
  %    \end{cvitems}
  %}

%---------------------------------------------------------


